mixchar

### 2021-03-03 README.Rmd
update for 2021

[![CRAN](http://www.r-pkg.org/badges/version/mixchar)
[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

>>>>

[![CRAN](http://www.r-pkg.org/badges/version/mixchar)
[![CRAN status](https://www.r-pkg.org/badges/version/mixchar)](https://CRAN.R-project.org/package=mixchar)
[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)
